Reply To Examiners

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

\begin{enumerate}
  \item each of the proposed models have their own name and
  \item not only the benefits are listed, but also their shortcomings.
\end{enumerate}

@@

The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
The chapter is also updated, so that new and existing references are added to provide direct support.
The author's publication list is now also included in this, as well as in the final conclusion, chapter.

>>>>

\begin{enumerate}
  \item Each of the proposed models have their own name and
  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
\end{enumerate}

@@

The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
This suggestion has been updated in this chapter, as well as through out the whole thesis.
The chapter is also updated, so that new and existing references are added to provide direct support.
The author's publication list is now also included in this chapter, as well as in the final conclusion chapter.
